Using reference models in variable selection \vspace{.1in}

### 2021-09-23 reviews/rebuttal.tex

% LaTeX rebuttal letter example. 
% 
% Copyright 2019 Friedemann Zenke, fzenke.net
%
% Based on examples by Dirk Eddelbuettel, Fran and others from 
% https://tex.stackexchange.com/questions/2317/latex-style-or-macro-for-detailed-response-to-referee-report
% 
% Licensed under cc by-sa 3.0 with attribution required.
% See https://creativecommons.org/licenses/by-sa/3.0/
% and https://stackoverflow.blog/2009/06/25/attribution-required/

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
%\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{xcolor}
\usepackage{hyperref}

% import Eq and Section references from the main manuscript where needed
% \usepackage{xr}
% \externaldocument{manuscript}

% package needed for optional arguments
\usepackage{xifthen}
% define counters for reviewers and their points
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% This refines the format of how the reviewer/point reference will appear.
\renewcommand{\thepoint}{P\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses
\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~Point~\thepoint} } ---\ }
   {\par }

\newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent 
	{\textbf{Reviewer~Point~\thepoint} } ---~#1\par }

\newenvironment{reply}
   {\medskip \noindent \begin{sf}\textbf{Reply}:\  }
   {\medskip \end{sf}}

\newcommand{\shortreply}[2][]{\medskip \noindent \begin{sf}\textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip \end{sf}}

\newcommand{\todo}{\subsection*{\textcolor{red}{To do (comment out when done)}:}}

\newcommand{\mm}[1]{\textcolor{red}{[M\aa ns: #1]}}
\newcommand{\av}[1]{\textcolor{blue}{[Aki: #1]}}
\newcommand{\ami}[1]{\textcolor{brown}{[Alonzo: #1]}}
\newcommand{\ts}[1]{\textcolor{purple}{[Tuomas: #1]}}

\begin{document}

\section*{Response to the reviewers}
% General intro text goes here
We thank the editor and the reviewers for careful review of the paper and the many useful comments.
\bigskip 
\hrule
\medskip 
\section*{Editor}

\paragraph{Editor comment}
I regret to inform you that the reviewers have raised serious concerns, and therefore your paper cannot be accepted for publication in Communications in Statistics – Theory and Methods. However since the reviewers do find some merit in the paper, I would be willing to reconsider if you wish to undertake major revisions and re-submit, addressing the referees' concerns.

\paragraph{Reply}

We thank the editor and the reviewer for the careful review of the paper and many valuable comments. We have addressed the discussed concerns and made changes to the manuscript accordingly. In particular, we have discussed the paper's practical implications and highlighted both the problem setting and the main contributions.

%\todo
%\begin{description}
%    \item [Mans] Nothing
%\end{description}

% Let's start point-by-point with Reviewer 1
\reviewersection

% Point one description 
\begin{point}
English language needs careful editing.
\end{point}

\begin{reply}
Thank you for the feedback. We have addressed now gone through the text multiple times and used automatic spell and grammar checkers. We are not native speakers, so please feel free to point out if you find further problems with the text.
\end{reply}

%\todo
%\begin{description}
%    \item[Mans] Clarified that we present first time how this problem should be approached in the Bayesian context.
%\end{description}

\begin{point}
The specific case considered in the article needs to be elaborated on in terms of its practical meaning and importance. Giving a solution for a specific case can be useful if that case has some practical importance. Otherwise, anyone can create solutions for many different cases.
\end{point}

\begin{reply}
We realise that the motivation of the work may be unclear. We aim to show one feasible (albeit simple) problem setting to show that it is possible to derive an unbiased variance estimator for the popular way of analysing the uncertainty in LOO-CV. Previous literature (e.g. Bengio and Grandvalet, 2004) indicates that this is not possible in general. To the best of our knowledge, we do not know anyone who has shown that it is possible to derive an unbiased estimator if one also considers the actual problem setting and model. This is an important advancement in the study for understanding the uncertainty in LOO-CV estimation in practice and can further encourage new work on variance estimation in Bayesian LOO-CV.

We now see that this has not been clear enough in the paper. We have clarified this both in the introduction and the discussion.
\end{reply}

\begin{point}
It is noted that there is no need for the observations to be identically distributed. We should see the impact of this on the likelihood in Eq. (6).
\end{point}

\begin{reply}
We see that the analysis description may be a bit misleading considering the two-level perspective on the variable $y$: the model level and the true data generating process level. In the latter, we apply only weak assumption on the distribution $p_\text{true}(y)$, and in particular, do not need to assume identically distributed observations. At the model level, the Bayesian normal model does make this assumption. Equation (6) defines the likelihood of the model. Based on the feedback, we clarified this in the text.
\end{reply}

\begin{point}
You have a normal hyper-prior on the mean $\theta$, $\sigma_{m}^{2}$ and $\sigma_{0}^{2}$ are fixed. Specification of these variances needs elaboration.
\end{point}

\begin{reply}
Thank you for this suggestion. We are a little unsure about what the reviewer asks for here. We added the following descriptive explanation on the effects of the parameters:

"The fixed data variance parameter $\sigma_\mathrm{m}^2$ reflects how the model considers the magnitude of the variability of the data. A fixed $\sigma_\mathrm{m}^2$ is mainly chosen to simplify derivations. The fixed prior variance parameter $\sigma_0^2$ reflects the prior belief of the magnitude of the variability of the unknown mean parameter. The fixed model parameters $\sigma_\mathrm{m}^2$ and $\sigma_0^2$ can be chosen freely."

In addition, we emphasise that the model may be miss-specified so that it represents the true data generating mechanism poorly.
\end{reply}

\begin{point}
The settings in the numerical example need further explanation. Why are those specific numbers selected? The example runs are too specific and cannot be generalised. This makes the article too focused on some specific cases. Then, the importance of dealing with these specific cases have to be articulated clearly.
\end{point}

\begin{reply}
Thank you for the relevant comment. We understand that the motivation of the experiments can be a bit confusing. The simulation experiment has two purposes. First, illustrating that the theory is correct and, second, show the naive estimator can be both upward and negatively biased.

The experiments apply three problem settings covering different, but feasible, scenarios including both well-fitting and bad-fitting data. We have now clarified the selection of the problem settings in the text. It is clear that, as the true data generating mechanism is quite unrestricted, there are arbitrarily many possible experiment setups. We believe that these applied setups are sufficient for illustrative purposes.

We believe that your comment calls for this to be written out more clearly in the paper. We have tried to clarify this further in the paper.
\end{reply}
\end{document}

### 2021-09-23 reviews/rebuttal_draft.txt

***Federico's quick comments:***

Reviewer 1: I think they misunderstood some of our results regarding the use of a reference model and not the specific implementation of projpred. Also about the complete selection case, our focus was on how the other methods improve with a reference model rather than the new projpred-based algorithm.  Apart from this inconvenient, I think that the other comments they report are interesting as the ones on reference model misspecification and prior sensitivity. I believe we have already addressed some of those, but maybe not that explicitly.

Reviewer 3: they don’t address major problems with the works, but mostly minor changes.

Associate Editor: also here, I think there has been a misunderstanding of the purpose of the complete selection section.

I didn’t receive any report by Reviewer 2.

What do you suggest to do next? I think that addressing the reviewers’s concerns would require to work mainly in two directions: we need to 
clarify that the purpose of the simulations is to show the effect of the reference model (and not a specific implementation) and than to answer questions 1)-5) by Reviewers 1. The latter requires a bit of thinking: I think we could mostly answer to those question in a discursive way, but would it be enough? Setting up experiments to study the reference model misspecification and the prior sensitivity problem might require some thinking!
To start, I could go in details through the reviews and the paper and try to write down for each question if we have already answered somewhere in the paper or what we should do. What do you think? I wait for your advice!

The deadline for the possible resubmission is the 23/02/22.

***Aki's quick comments***

Quick comments that need to be processed to be polite answers (I wrote these before looking at Federico's comments)

Reviewer #1 (PDF reviewer?)

The reviewer has mistaken that we would be proposing a new method. The main purpose is as stated in the abstract:
"In several numerical experiments, we investigate the performance of the projective prediction approach as well as alternative variable selection methods with and without reference models. Our results indicate that the use of reference models generally translates into better and more stable variable selection."

We need to clarify this point. We knew that projpred works well for the minimal set variable selection, but we didn't know whether that is due to the use of reference model or due to the projection that make better inference after the selection. In this paper we show that the use of a reference model helps also other approaches and thus it canät be the projection alone that is producing the good results. Other point we make is that projpred was specifically designed for the minimal set variable selection and we show that it is not good for complete set selection, which is useful information, too. Showing a failure mode of existing algorithm is useful even without being able to develop a solutin for that failure.

We should clarify these issues and resbumit without better approach. I would assume the second round decision would be quicker.

For the last comment I would answer that, of course the performance of the variable selection depends on the quality of the reference model. If the reference model is, e.g., without any covariates, there is no useful information to learn. Stability of Bayesian inference wrt priors have been extensively studied elsewhere and the prior sensitivity checking is natural part of the workflow for building a reference model (cite Bayesian workflow, priorsense paper, and something else)

Reviewer #3

They also comment that " the motivation of the study in relation to
the literature is missing in the Introduction. " and we need to
clarify the poimt I mentioned above. They helpfully point out that
"Full motivation is given in Section 2. However, it needs to be
briefly mentioned in the Introduction as well to motivate the reader
to keep reading. In addition, instead of pointing to the references,
please give a brief critique of them." so we need to just copy stuff
from there.

> 2. Please include the computational cost of compared approaches in Section 2.1.

Sensible suggestion.

> 3. Please add a brief summary of the results you obtained in Section 3 and the main message you infer from these results before moving onto Section 4.

Sensible suggestion.

> 4. Please mention the availability of the R codes to reporoduce the results under each section as well.

Sensible suggestion.

AE

> Associate Editor: Please note the strong concerns of the
> reviewers. If you cannot implement a better projective prediction
> approach for complete variable selection problems, then at the very
> least, I would expect you to motivate why it's worth knowing about
> this approach; you show that it doesn't work very well.

I think the above answers cover this, too.

Overall the reviewer #3 seems to be positive, and also helpfully hints
why reviewer #1 may be confused.

I agree with Federico's analysis of the situation

 - Clarify as suggested by reviewer #3
 - Transform the comments about reviewr #1 to polite explanation how we have improved the paper and clarified the main points.
 - we can be more straight that iterative projpred is not that good

***Juho's quick comments***

I generally agree with Aki's comments, in particular that we should
not try to come up with a better algorithm for complete variable
selection, but try to articulate why this study still contains useful
findings (negative results are also useful, it's sad how often they
are overlooked).

A few comments to the points raised by reviewer 1 (should be
reformulated to be polite answers):

"... you can have use standard inverted gamma priors on sigma2 and
tau2 by determining the parameters of the prior in order to the prior
mixture gives reasonable results about the data using the prior
mixture. How can you study the robustness of your results to this
important aspect?"
- I have to admit that I did not understand what the reviewer is
trying to say here.

"Perhaps a solution to the previous problem would be to determine the
reference model using frequentist MLE procedures that avoid the
construction of prior distributions and use a single point prediction
or, alternatively, to use the sampling distribution of MLE as a
posterior distribution and take this “Bayesian” model as reference
model. Do you have any experience in this line?"
- I don't really have experience about this, but I don't quite see how
a frequentist reference model would solve the issue of having to
choose the prior for the reference model; afterall you need to choose
how you regularize your frequentist model, which is kinda equivalent
to choosing the prior (but you lose the extra regularizing effect
which comes from integrating over the posterior uncertainty in a
Bayesian model).

"What if the true generator process is a mixture model, in such a way
that there is not a unique solution to the minimal subset variable
selection problem? In fact, how can you assure that the minimal subset
variable selection problems have only one selection?"
- I don't think we have stated anywhere that we assume there is a
unique solution? Nor do we attempt to find such unique solution. We
attempt to find _a_ model with smallest number of variables without
substantial loss in predictive accuracy compared to the reference or
any other candidate model.

"In most of real situations, we have an M-open problem (particularly
in big data problems) where the true generator mechanism is too
complex and it is not included in the family of considered models.
What would be the performance of your methodology if the reference
model is far from the true generator process? How can you detect these
situations?"
- Not sure what we should answer here, but it feels to me that
answering this sort of question would require a paper (or two) on its
own. We can write e.g. that this is beyond the scope of this paper,
and we feel it's not quite fair to require such a major issue to be
solved in the present paper.

"Section 4.1: It is no clear how the value of alpha should be chosen.
alpha = 0.16 is a magic number and a more thoroughly discussion of the
influence of this value should be provided."
- It is purely heuristic, yes, but the 'magic' number comes from the
fact that if each tail has 16% mass, then the central interval has 68%
mass which corresponds to plus minus one std assuming normal
distribution (i.e. alpha=0.16 corresponds to one std away from mean,
thus it's not that magical).

### 2021-09-23 reviews/rebuttal_draft.txt

We need to clarify this point. We knew that projpred works well for the minimal set variable selection, but we didn't know whether that is due to the use of reference model or due to the projection that make better inference after the selection. In this paper we show that the use of a reference model helps also other approaches and thus it canät be the projection alone that is producing the good results. Other point we make is that projpred was specifically designed for the minimal set variable selection and we show that it is not good for complete set selection, which is useful information, too. Showing a failure mode of existing algorithm is useful even without being able to develop a solutin for that failure.

We should clarify these issues and resbumit without better approach. I would assume the second round decision would be quicker.

For the last comment I would answer that, of course the performance of the variable selection depends on the quality of the reference model. If the reference model is, e.g., without any covariates, there is no useful information to learn. Stability of Bayesian inference wrt priors have been extensively studied elsewhere and the prior sensitivity checking is natural part of the workflow for building a reference model (cite Bayesian workflow, priorsense paper, and something else)

Related to point 1)

The reference model doesn't need to be Bayesian. The results are better with better model. The sensitivity of the Bayesian models to choice of priors is well studied and there exists well developed workflows for doing prior sensitivity analysis and other model checking (see, e.g. Gelman et al, 2020). In this paper the point is not the Bayesian workflow, but to analysis given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be imporvef by relacing the data with filtered prediction from the reference model. We have added clarification that the reference model approach requires a sensible model, so that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.

@@

"What if the true generator process is a mixture model, in such a way
that there is not a unique solution to the minimal subset variable
selection problem? In fact, how can you assure that the minimal subset
variable selection problems have only one selection?"
- I don't think we have stated anywhere that we assume there is a
unique solution? Nor do we attempt to find such unique solution. We
attempt to find _a_ model with smallest number of variables without
substantial loss in predictive accuracy compared to the reference or
any other candidate model.

"In most of real situations, we have an M-open problem (particularly
in big data problems) where the true generator mechanism is too
complex and it is not included in the family of considered models.
What would be the performance of your methodology if the reference
model is far from the true generator process? How can you detect these
situations?"
- Not sure what we should answer here, but it feels to me that
answering this sort of question would require a paper (or two) on its
own. We can write e.g. that this is beyond the scope of this paper,
and we feel it's not quite fair to require such a major issue to be
solved in the present paper.

"Section 4.1: It is no clear how the value of alpha should be chosen.
alpha = 0.16 is a magic number and a more thoroughly discussion of the
influence of this value should be provided."
- It is purely heuristic, yes, but the 'magic' number comes from the
fact that if each tail has 16% mass, then the central interval has 68%
mass which corresponds to plus minus one std assuming normal
distribution (i.e. alpha=0.16 corresponds to one std away from mean,
thus it's not that magical).

***23 September 2021***

We have added clarification that the reference model approach requires a sensible model, so that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models. A sensible reference model doesn't need to be Bayesian. The results are better with better reference models. The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking (see, e.g. Gelman et al, 2020). In this paper the point is not the Bayesian workflow, but to analysis given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model. The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues. As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.

MLE is more unstable than Bayesian approach. The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors. We have added references that discuss merits of Bayesian approach compared to MLE. Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it’s a good predictive model, it will be a useful reference model.

The projection predictive variable selection and its properties have been extensively discussed in Piironen & Vehtari, and Piironen, Paasiniemi & Vehtari, and we refer to them for the detailed discussion on the uncertainty related to search paths. Paasinemi (2018) https://aaltodoc.aalto.fi/handle/123456789/33657 provides illustrations how this uncertainty can be communicated to the users. When there are correlating variables that have exactly the same amount of information, the minimal set is not unique. In this paper, we focused on the average performance of the minimal set, but when analysing a single dataset, we recommend the approaches presented in Paasinemi (2018) to analyse alternative possible variable sets.

We assume that all models are wrong. Analysing model misspecification is well studied in Bayesian literature and there are plenty of methods available for model checking (see, e.g. Gelman et al, 2020). The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building (Gelman et al, 2020). Even a misspecifed model that would introduce some bias can reduce the variance so that the variable selection is improved.

See Piironen, Paasiniemi & Vehtari,

The usual Bayesian workflow (Gelman et al, 2020) states that if there is uncertainty about which model then we integrate over the model space or create a continuous super model that includes the alternative models as special cases.

We used AIC because reference X was using AIC. The goal of the paper was not to compare all possible information criteria. We made choices to keep the paper within reasonable length. Based on the results, we assume that variable selection using any *IC approach will benefit from using a reference model.

> M Complete approach, it is usually consistent.

It seems your definition of M-complete doesn’t match with definition of Bernardo & Smith (1994) we are using.

### 2021-11-02 paper/ref_approach.tex
minor changes from the reviewers comments: typos and availability of repo

In this section, we will provide an initial motivation and intuition 
for the use of reference models to improve variable selection methods.
We will start with a case study that is repeatedly used throughout
the paper to illustrate the benefits of reference models before we dive deeper
into the theoretical reasons why reference models help in variable selection.

@@

In the body fat example above, our two simultaneous goals were to 
obtain good predictive performance and to select a smaller number of variables. 
When the goal is to select a minimal subset of variables,
which have similar predictive performance as the full model, we call it
\emph{minimal subset variable selection}. This minimal subset might
exclude variables which have some predictive information about the
target but, given the minimal subset, these variables are not able to
provide such additional information that would improve predictive
performance in a substantial manner.
The usual reason for this is that the relevant variables
which are not in the minimal subset are highly correlated with variables already in
the minimal subset. We will return to a problem of finding all
the variables with some predictive power in Section~\ref{complete-selection}.

@@

Using the data generating mechanism \eqref{eq:simulated_data}, we
simulate data sets of different sizes with a relatively large number
of variables $p=70$, with $k=20$ of them being predictive.  We compare
the minimal subset variable selection performance of the projection
predictive approach (which uses a reference model and it is referred to as projpred), 
a Bayesian stepwise
forward selection with and without a reference model, and maximum
likelihood stepwise forward selection with and without a reference
model (steplm). The following is a summary of the implementation of the compared methods:
\begin{itemize}
\item \textbf{projpred}: the projective prediction approach is used. 
  The reference model is a Bayesian linear regression
  model using the first five supervised principal components \citep{piironen2018} as predictors
  and the full posterior predictive distribution as the basis of the projection.   
  The search heuristic  is forward search and the predictive performance 
  is estimated via 10-fold cross-validation. The selection continues
  until the predictive performance is close to the predictive
  performance of the reference model. See more details in Appendix A.

@@

An alternative to minimal subset variable selection is \emph{complete
  variable selection} in which the goal is to find all relevant
variables that have some predictive information about the target. In
complete variable selection, it is possible that there are theoretically
relevant variables, but given finite noisy data we are not able to infer their relevance.
The projection predictive approach was originally designed for the minimal subset
variable selection but we will test a simple iterative variant for the complete
variable selection case in this Section.
 In addition, we analyse the benefits of the reference
model approach in combination with three other
methods which have been specifically designed for complete variable selection. 
As the criteria of selection performance, we evaluate the average false
discovery rate and the average
sensitivity (i.e., the ratio of the number of relevant selected
variables over the total number of relevant variables). We also provide
a comparison of the stability of the selection by means of a stability
measure proposed by \citet{paper:stability}, which goes from 0 to 1 and a higher value 
means a more stable selection.

@@

\begin{center}
\begin{algorithm}[H]
\SetAlgoLined
\KwResult{$R:=\{\text{selected variables}\}$}
 $F:=\{\text{set of variables}\}$ \;
 $R=\{\emptyset\}$ \;
 Fit reference model\;
 \While{$F\neq\{\emptyset\}$}{
   projection.HeuristicSearch() \;
   projection.elpdEstimate() \;
   $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{base}}>0)\geq\alpha)$\} \;

@@

In the experiments shown in the next sections, we include an additional iterative
method which we refer to as `iterative lasso'. It consists of the same iterative
algorithm as iterative projpred expect for not using any reference model, but
the lasso method for variable selection, instead.
That is, it uses the observed target values instead of predictions of the reference model.
The comparison with iterative lasso can help to disentangle the effects
of the iterative procedure and the usage of a reference model in complete feature selection.

>>>>

In this section, we will provide an initial motivation and intuition 
for the use of reference models to improve variable selection methods.
We will start with a case study that is repeatedly used throughout
the paper to illustrate the benefits of reference models before we dive deeper
into the theoretical reasons why reference models help in variable selection.
\\
The code to run all
the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.

@@

In the body fat example above, our two simultaneous goals were to 
obtain good predictive performance and to select a smaller number of variables. 
When the goal is to select a minimal subset of variables,
which have similar predictive performance as the full model, we call it
\emph{minimal subset variable selection}. This minimal subset might
exclude variables which have some predictive information about the
target but, given the minimal subset, these variables are not able to
provide such additional information that would improve predictive
performance in a substantial manner.
The usual reason for this is that the relevant variables
which are not in the minimal subset are highly correlated with variables already in
the minimal subset. We will return to a problem of finding all
the variables with some predictive power in Section~\ref{complete-selection}.
\\
The code to run all
the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.

@@

Using the data generating mechanism \eqref{eq:simulated_data}, we
simulate data sets of different sizes with a relatively large number
of variables $p=70$, with $k=20$ of them being predictive.  We compare
the minimal subset variable selection performance of the projection
predictive approach (which uses a reference model and it is referred to as projpred), 
a Bayesian stepwise
backward selection with and without a reference model, and maximum
likelihood stepwise backward selection with and without a reference
model (steplm). The following is a summary of the implementation of the compared methods:
\begin{itemize}
\item \textbf{projpred}: the projective prediction approach is used. 
  The reference model is a Bayesian linear regression
  model using the first five supervised principal components \citep{piironen2018} as predictors
  and the full posterior predictive distribution as the basis of the projection.   
  The search heuristic  is forward search and the predictive performance 
  is estimated via 10-fold cross-validation. The selection continues
  until the predictive performance is close to the predictive
  performance of the reference model. See more details in Appendix A.

@@

An alternative to minimal subset variable selection is \emph{complete
  variable selection} in which the goal is to find all relevant
variables that have some predictive information about the target. In
complete variable selection, it is possible that there are theoretically
relevant variables, but given finite noisy data we are not able to infer their relevance.
The projection predictive approach was originally designed for the minimal subset
variable selection but we will test a simple iterative variant for the complete
variable selection case in this Section.
 In addition, we analyse the benefits of the reference
model approach in combination with three other
methods which have been specifically designed for complete variable selection. 
As the criteria of selection performance, we evaluate the average false
discovery rate and the average
sensitivity (i.e., the ratio of the number of relevant selected
variables over the total number of relevant variables). We also provide
a comparison of the stability of the selection by means of a stability
measure proposed by \citet{paper:stability}, which goes from 0 to 1 and a higher value 
means a more stable selection. 
\\
The code to run all
the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.

@@

\begin{center}
\begin{algorithm}[H]
\SetAlgoLined
\KwResult{$R:=\{\text{selected variables}\}$}
 $F:=\{\text{set of variables}\}$ \;
 $R=\{\emptyset\}$ \;
 Fit reference model\;
 \While{$F\neq\{\emptyset\}$}{
   projection.HeuristicSearch() \;
   projection.elpdEstimate() \;
   $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{best}}>0)\geq\alpha)$\} \;

@@

In the experiments shown in the next sections, we include an additional iterative
method which we refer to as `iterative lasso'. It consists of the same iterative
algorithm as iterative projpred except for not using any reference model, but
the lasso method for variable selection, instead.
That is, it uses the observed target values instead of predictions of the reference model.
The comparison with iterative lasso can help to disentangle the effects
of the iterative procedure and the usage of a reference model in complete feature selection.
